---
title: "Minicensus report"
author: "www.databrew.cc"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
  pdf_document: default
---


```{r setup, include=FALSE, echo = FALSE}
# Basic knitr options
library(knitr)
opts_chunk$set(comment = NA, 
               # echo = FALSE, 
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE,
               fig.width = 9.64,
               fig.height = 5.9,
               fig.path = 'figures/')
```

```{r}
#!/usr/bin/Rscript
start_time <- Sys.time()
message('System time is: ', as.character(start_time))
message('---Timezone: ', as.character(Sys.timezone()))
keyfile_path <- '../../credentials/bohemia_pub.pem'
creds_fpath <- '../../credentials/credentials.yaml'
creds <- yaml::yaml.load_file(creds_fpath)
suppressMessages({
  library(RPostgres)
  library(bohemia)
  library(yaml)
  library(dplyr)
  library(ggplot2)
  library(leaflet)
  library(leaflet.extras)
  library(leafgl)
  library(readr)
  library(tidyr)
  library(DT)
  library(sf)
  library(gsheet)
  theme_bohemia <- ggplot2::theme_bw
  theme_set(theme_bohemia())
}
)

# get app functions (specifically for traccar data)
source('../../rpackage/bohemia/R/app_functions.R')

if(!'gps.RData' %in% dir()){
  gps <- gsheet::gsheet2tbl('https://docs.google.com/spreadsheets/d/1hQWeHHmDMfojs5gjnCnPqhBhiOeqKWG32xzLQgj5iBY/edit#gid=1016618615')
  save(gps, file = 'gps.RData')
} else {
  load('gps.RData')
}

is_local <- FALSE
drv <- RPostgres::Postgres()
# read in credenstials 
creds <- yaml::yaml.load_file('../../credentials/credentials.yaml')


if(is_local){
  con <- dbConnect(drv, dbname='bohemia')
} else {
  psql_end_point = creds$endpoint
  psql_user = creds$psql_master_username
  psql_pass = creds$psql_master_password
  con <- dbConnect(drv, dbname='bohemia', host=psql_end_point, 
                   port=5432,
                   user=psql_user, password=psql_pass)
}

replace_local_files <- TRUE
if(replace_local_files){
  remove_file <- '/tmp/Mozambique_efficient_local.RData'
  if(file.exists(remove_file)){
    file.remove(remove_file)
  }
  remove_file <- '/tmp/Tanzania_efficient_local.RData'
  if(file.exists(remove_file)){
    file.remove(remove_file)
  }
  
  use_cached <- TRUE
  for(the_country in c('Mozambique', 'Tanzania')){
    the_iso <- ifelse(the_country == 'Mozambique', 'moz', 'tza')
    out <- load_odk_data(local = is_local, the_country = the_country, efficient = TRUE, use_cached = use_cached, con = con)
    assign(the_iso, out, envir = .GlobalEnv)
  }
}

# Define a default fieldworkers data
if(!'fids.csv' %in% dir('/tmp')){
  fids_url <- 'https://docs.google.com/spreadsheets/d/1o1DGtCUrlBZcu-iLW-reWuB3PC8poEFGYxHfIZXNk1Q/edit#gid=0'
  fids1 <- gsheet::gsheet2tbl(fids_url) %>% dplyr::select(bohemia_id, first_name, last_name, supervisor) %>% dplyr::mutate(country = 'Tanzania')
  fids_url <- 'https://docs.google.com/spreadsheets/d/1o1DGtCUrlBZcu-iLW-reWuB3PC8poEFGYxHfIZXNk1Q/edit#gid=490144130'
  fids2 <- gsheet::gsheet2tbl(fids_url) %>% dplyr::select(bohemia_id, first_name, last_name, supervisor) %>% dplyr::mutate(country = 'Mozambique')
  fids_url <- 'https://docs.google.com/spreadsheets/d/1o1DGtCUrlBZcu-iLW-reWuB3PC8poEFGYxHfIZXNk1Q/edit#gid=179257508'
  fids3 <- gsheet::gsheet2tbl(fids_url) %>% dplyr::select(bohemia_id, first_name, last_name, supervisor) %>% dplyr::mutate(country = 'Catalonia')
  fids <- bind_rows(fids1, fids2, fids3)
  readr::write_csv(fids, '/tmp/fids.csv')
} else {
  fids <- readr::read_csv('/tmp/fids.csv')
}

# get traccar data
if(!'traccar_tz.csv' %in% dir('/tmp')){
  traccar <- dbReadTable(conn = con, name = 'traccar')
  # get traccar data
  traccar <- separate(data = traccar, col = 'valid', into = c('battery', 'distance', 'total_distance', 'motion'), sep = ' ')
  traccar$battery <- as.numeric(unlist(lapply(strsplit(traccar$battery, ':'), function(x) x[2])))
  traccar$distance <- as.numeric(unlist(lapply(strsplit(traccar$distance, ':'), function(x) x[2])))
  traccar$total_distance <- as.numeric(unlist(lapply(strsplit(traccar$total_distance, ':'), function(x) x[2])))
  traccar$motion <- as.character(unlist(lapply(strsplit(traccar$motion, ':'), function(x) x[2])))
  
  traccar_moz <- traccar %>% filter(unique_id %in% fids$bohemia_id[fids$country == 'Mozambique'])
  traccar_tz <- traccar %>% filter(unique_id %in% fids$bohemia_id[fids$country == 'Tanzania'])
  rm(traccar)
  readr::write_csv(traccar_tz, '/tmp/traccar_tz.csv')
  readr::write_csv(traccar_moz, '/tmp/traccar_moz.csv')

} else {
  traccar_moz <- readr::read_csv('/tmp/traccar_moz.csv')
  traccar_tz <- readr::read_csv('/tmp/traccar_tz.csv')
}

# get anomalies and errors
if(!'an_tz.csv' %in% dir('/tmp')){
  an_tz<- dbGetQuery(conn = con, statement = "SELECT * FROM anomalies WHERE country = 'Tanzania'")
  an_moz<- dbGetQuery(conn = con, statement = "SELECT * FROM anomalies WHERE country = 'Mozambique'")
 
  readr::write_csv(an_tz, '/tmp/an_tz.csv')
  readr::write_csv(an_moz, '/tmp/an_moz.csv')
} else {
  an_moz <- readr::read_csv('/tmp/an_moz.csv')
  an_tz <- readr::read_csv('/tmp/an_tz.csv')
}

x = dbDisconnect(con)

# Function for extracting lng and lat from a odk geocode object
extract_ll <- function(x){
  lngs <- lats <- c()
  for(i in 1:length(x)){
    y <- x[i]
    lat <- unlist(lapply(strsplit(y[1], ' '), function(z){z[1]}))
    lng <- unlist(lapply(strsplit(y[1], ' '), function(z){z[2]}))
    lngs[i] <- lng; lats[i] <- lat
  }
  
  lng <- as.numeric(lngs); lat <- as.numeric(lats)
  return(tibble(lng = lng, lat = lat))
}

# Define "targets"
targets <- gps %>%
  filter(clinical_trial == 0) %>%
  group_by(iso) %>%
  summarise(n_households = sum(n_households)) %>%
  ungroup %>%
  mutate(country = ifelse(iso == 'MOZ', 'Mozambique', 'Tanzania')) %>%
  mutate(n_households = ifelse(iso == 'MOZ', 30803, n_households)) # manual adjustment
```

```{r}
# Combine data
odk_data <- list()
odk_data$data <- list()
for(i in 1:length(moz)){
  odk_data$data[[i]] <- 
    bind_rows(moz[[i]] %>% mutate(iso = 'MOZ'),
              tza[[i]] %>% mutate(iso = 'TZA'))
}
names(odk_data$data) <- names(moz)
```



# Data collection progress {.tabset}

## Overall

### Chart: Household minicensus forms collected

Red line: Cumulative; Bars: Weekly sum; Dotted line: Forward projection (linear regression); Orange line: recon-estimated total number of households

```{r, fig.height = 8}
pd <- odk_data$data$minicensus_main %>%
  group_by(date = lubridate::floor_date(todays_date, 'week'),
           country = hh_country) %>%
  tally %>%
  ungroup %>%
  group_by(country) %>%
  mutate(cs = cumsum(n))

# Build a regression
fit <- lm(cs ~ date + country, data = pd)
# Build a prediction df
pred_df <- 
  expand.grid(date = seq(min(pd$date),
                         as.Date('2021-12-05'),
                         by = 'week'),
              country = sort(unique(pd$country)))
pred_df$y <- predict(fit, newdata = pred_df)
pred_df$remove <- 
  pred_df$country == 'Mozambique' &
           pred_df$y > targets$n_households[targets$country == 'Mozambique'] |
  pred_df$country == 'Tanzania' &
           pred_df$y > targets$n_households[targets$country == 'Tanzania']
pred_df <- pred_df %>% filter(!remove)


ggplot(data = pd,
       aes(x = date)) +
  geom_line(aes(y = cs),
            color = 'red') +
  # geom_point(aes(y = cs),
  #           color = 'red') +
  geom_bar(aes(y = n),
               fill = 'black',
           stat = 'identity') +
  theme_bohemia() +
  facet_wrap(~country, ncol = 1) +
  theme(legend.position = 'none') +
  labs(x = 'Week',
       y = 'Minicensus forms') +
  geom_line(data = pred_df,
            aes(x = date,
                y = y),
            lty = 2) +
  geom_hline(data = targets,
            aes(yintercept = n_households),
            color = 'darkorange',
            alpha = 0.5)
```


### Map: Household minicensus forms collected

```{r}
geo_dat <-
  odk_data$data$enumerations %>%
              mutate(hh_id = agregado,
                     hh_geo_location = location_gps,
                     status = 'Enumerated') %>%
  bind_rows(
    odk_data$data$refusals %>%
      # filter(iso == 'MOZ') %>% 
      mutate(status = 'Refused')
  )  %>%
  bind_rows(
      odk_data$data$minicensus_main %>%
  # filter(iso == 'MOZ') %>% 
  mutate(status = 'Minicensed')
  ) %>%
  dplyr::select(hh_geo_location,
                status,
                hh_id) 



ll <- extract_ll(geo_dat$hh_geo_location)
geo_dat$lng <- ll$lng; geo_dat$lat <- ll$lat
geo_dat <- geo_dat %>%
  mutate(x = lng,
         y = lat) %>%
  filter(!is.na(lng), !is.na(lat)) %>%
  filter(lng > 5,
         lat < 0)
pts <- st_as_sf(data.frame(geo_dat), coords = c("lng", "lat"), crs = 4326)
leaflet() %>%
  addProviderTiles(providers$Esri.WorldImagery) %>%
                  addGlPoints(data = pts,
                            # fillColor = 'red',
                            fillColor = pts$status,
                            popup = pts,
                            group = "pts") %>%
                addLegend("bottomright", 
                          colors =c("#FFFF00",  "#871F78", "#00FFFF"),
                          labels= c("Refused", "Enumerated","Minicensed"),
                          title= "Status",
                          opacity = 1)
```



### Table: Household minicensus forms collected

```{r}
x <-odk_data$data$minicensus_main %>%
  group_by(date = todays_date,
           country = hh_country) %>%
  tally %>%
  ungroup %>%
  group_by(country) %>%
  mutate(cs = cumsum(n)) %>%
  dplyr::select(-cs) %>%
  tidyr::spread(key = country, value = n)
bohemia::prettify(x, nrows = nrow(x), download_options = TRUE)
```

: gps stuff, fw performance, errors and anomalies, etc (look in the app)

## Daily submissions

### Daily minicensus forms

```{r}
# get forms 
odk_data$data$minicensus_main %>%
  mutate(week = lubridate::week(todays_date)) %>%
  group_by(hh_country, todays_date) %>% 
  summarise(counts = n()) %>% 
  ggplot(aes(todays_date, counts)) + 
  # scale_fill_manual(name = '', values = c("darkorange",  "#871F78")) +
  geom_bar(stat='identity', position = 'dodge') +
  labs(x = '', y = 'Minicensus forms submitted') +
  facet_wrap(~hh_country, ncol = 1)
```

### Daily VA forms

```{r}
# get forms 
odk_data$data$va %>%
  mutate(week = lubridate::week(todays_date),
         country = ifelse(iso=='MOZ', 'Mozambique', 'Tanzania')) %>%
  group_by(country, todays_date) %>% 
  summarise(counts = n()) %>% 
  ggplot(aes(todays_date, counts)) + 
  # scale_fill_manual(name = '', values = c("darkorange",  "#871F78")) +
  geom_bar(stat='identity', position = 'dodge') +
  labs(x = '', y = 'VA forms submitted') +
  facet_wrap(~country, ncol = 1)
```

### Daily Enumeration forms (Mozambique only)

```{r}
# get forms 
odk_data$data$enumerations %>%
  mutate(week = lubridate::week(todays_date),
         country = ifelse(iso=='MOZ', 'Mozambique', 'Tanzania')) %>%
  group_by(country, todays_date) %>% 
  summarise(counts = n()) %>% 
  ggplot(aes(todays_date, counts)) + 
  # scale_fill_manual(name = '', values = c("darkorange",  "#871F78")) +
  geom_bar(stat='identity', position = 'dodge') +
  labs(x = '', y = 'VA forms submitted') +
  facet_wrap(~country, ncol = 1)
```

## Tracking fieldworkers

### Most recent location (Tanzania)

```{r}
  traccar_tz$date <- as.Date(traccar_tz$devicetime, 'EST')
 
  out <- traccar_tz %>%
    mutate(bohemia_id = as.numeric(as.character(unique_id))) %>%
    left_join(fids %>% dplyr::select(bohemia_id, 
                                     first_name, 
                                     last_name)) %>%
    mutate(Fieldworker = paste0(bohemia_id, ' ',
                                first_name, ' ',
                                last_name)) %>%
    group_by(Fieldworker) %>%
    filter(devicetime == max(devicetime))
  
  leaflet() %>%
    addTiles() %>%
    addMarkers(data = out,
               popup = paste0(out$Fieldworker, ' ',
                              out$devicetime)) 


```

### Most recent location (Mozambique)

```{r}
  traccar_moz$date <- as.Date(traccar_moz$devicetime, 'EST')
 
  out <- traccar_moz %>%
    mutate(bohemia_id = as.numeric(as.character(unique_id))) %>%
    left_join(fids %>% dplyr::select(bohemia_id, 
                                     first_name, 
                                     last_name)) %>%
    mutate(Fieldworker = paste0(bohemia_id, ' ',
                                first_name, ' ',
                                last_name)) %>%
    group_by(Fieldworker) %>%
    filter(devicetime == max(devicetime))
  
  leaflet() %>%
    addTiles() %>%
    addMarkers(data = out,
               popup = paste0(out$Fieldworker, ' ',
                              out$devicetime)) 

```

### Tracking history one month (Tanzania)

```{r}
  todays_date <- Sys.Date()
  last_month <- todays_date -30
  traccar_tz$date <- as.Date(traccar_tz$devicetime, 'EST')
  traccar_tz$time_of_day <- lubridate::round_date(traccar_tz$devicetime, 'hour')
  traccar_tz$day <- lubridate::round_date(traccar_tz$devicetime, 'day')
  traccar_tz$time_of_day <- as.character(traccar_tz$time_of_day)
  traccar_tz$day <- as.character(traccar_tz$day)
  
  out <- traccar_tz %>%
    mutate(bohemia_id = as.numeric(as.character(unique_id))) %>%
    left_join(fids %>% dplyr::select(bohemia_id, 
                                     first_name, 
                                     last_name)) %>%
    mutate(Fieldworker = paste0(bohemia_id, ' ',
                                first_name, ' ',
                                last_name))
                                
  out <- out %>%
    group_by(Fieldworker) %>%
    filter(date >= last_month) %>%
    summarise(Pings = n(),
              `Total KM recorded` = round(sum(distance/1000, na.rm = TRUE)),
              `Average battery life` = paste0(round(mean(battery, na.rm=TRUE), 2), ' %'))
  DT::datatable(out)

```

### Tracking history one month (Mozambique)

```{r}
  todays_date <- Sys.Date()
  last_month <- todays_date -30
  traccar_moz$date <- as.Date(traccar_moz$devicetime, 'EST')
  traccar_moz$time_of_day <- lubridate::round_date(traccar_moz$devicetime, 'hour')
  traccar_moz$day <- lubridate::round_date(traccar_moz$devicetime, 'day')
  traccar_moz$time_of_day <- as.character(traccar_moz$time_of_day)
  traccar_moz$day <- as.character(traccar_moz$day)
  
  out <- traccar_moz %>%
    mutate(bohemia_id = as.numeric(as.character(unique_id))) %>%
    left_join(fids %>% dplyr::select(bohemia_id, 
                                     first_name, 
                                     last_name)) %>%
    mutate(Fieldworker = paste0(bohemia_id, ' ',
                                first_name, ' ',
                                last_name))
  out <- out %>%
    group_by(Fieldworker) %>%
    filter(date >= last_month) %>%
    summarise(Pings = n(),
              `Total KM recorded` = round(sum(distance/1000, na.rm = TRUE)),
              `Average battery life` = paste0(round(mean(battery, na.rm=TRUE), 2), ' %'))
  DT::datatable(out)

```


## Errors and anomalies

### Over time

```{r}
an <- rbind(an_tz, an_moz)
an %>% 
  group_by(country,date) %>% 
  filter(date>'2019-01-01') %>%
  summarise(`# of anomalies` = sum(type == 'error', na.rm=TRUE),
            `# of errors` = sum(type == 'anomaly', na.rm=TRUE)) %>%
  gather(key=key, value=value, -date,-country) %>%
  mutate(date = as.Date(date)) %>%
  group_by(key) %>%
  mutate(`cumulative_value` = cumsum(value)) %>%
  ggplot(aes(date, value, fill=key)) +
  geom_bar(stat = 'identity') +
  scale_fill_manual(name = '', 
                    values = c('black', 'grey')) +
  labs(x='Date', y='') +
  theme_bohemia() + facet_wrap(~country, ncol = 1)

```

### Corrections Tanzania

```{r}

corrections <- odk_data$data$corrections %>% filter(iso == 'TZA')
fixes <- odk_data$data$fixes%>% filter(iso == 'TZA')
# save(anomalies, corrections, fixes, file = '/tmp/this.RData')

joined <- left_join(an_tz,
                    corrections %>% dplyr::select(-instance_id))
joined <- left_join(joined, fixes)

pd <- joined %>%
  mutate(status = ifelse(!is.na(done_by), 'Done',
                         ifelse(!is.na(response_details), 'Response submitted',
                                'Needs response'))) %>%
  group_by(category = status) %>%
  tally %>%
  ungroup %>%
  mutate(fraction = n/ sum(n)) %>%
  mutate(p = paste0(round(fraction * 100, digits = 1), '%')) %>%
  mutate(ymax = cumsum(fraction)) %>%
  mutate(ymin = c(0, head(ymax, n = -1))) %>%
  mutate(label_position = (ymax + ymin) / 2) %>%
  mutate(label = paste0(category, '\nN: ', n, ' (', p, ')'))

cols <- c('darkgreen', grey(0.5),'darkorange')
ggplot(data = pd, aes(ymax=ymax, ymin=ymin, xmax=4, xmin=2, fill=category)) +
  geom_rect(alpha = 0.6) +
  ggrepel::geom_text_repel( x=5, aes(y=label_position, label=label, color = category), size=4) +
  coord_polar(theta="y") +
  xlim(c(-1, 4)) +
  theme_void() +
  # scale_fill_brewer(palette=4) +
  scale_fill_manual(name = '',
                    values = cols) +
  scale_color_manual(name = '',
                     values = cols) +
  theme(legend.position = "none") +
  labs(x = '',
       y = '',
       title = 'Anomalies/errors status')
```

### Corrections Mozambique

```{r}

corrections <- odk_data$data$corrections %>% filter(iso == 'MOZ')
fixes <- odk_data$data$fixes%>% filter(iso == 'MOZ')
# save(anomalies, corrections, fixes, file = '/tmp/this.RData')

joined <- left_join(an_moz,
                    corrections %>% dplyr::select(-instance_id))
joined <- left_join(joined, fixes)

pd <- joined %>%
  mutate(status = ifelse(!is.na(done_by), 'Done',
                         ifelse(!is.na(response_details), 'Response submitted',
                                'Needs response'))) %>%
  group_by(category = status) %>%
  tally %>%
  ungroup %>%
  mutate(fraction = n/ sum(n)) %>%
  mutate(p = paste0(round(fraction * 100, digits = 1), '%')) %>%
  mutate(ymax = cumsum(fraction)) %>%
  mutate(ymin = c(0, head(ymax, n = -1))) %>%
  mutate(label_position = (ymax + ymin) / 2) %>%
  mutate(label = paste0(category, '\nN: ', n, ' (', p, ')'))

cols <- c('darkgreen', grey(0.5),'darkorange')
ggplot(data = pd, aes(ymax=ymax, ymin=ymin, xmax=4, xmin=2, fill=category)) +
  geom_rect(alpha = 0.6) +
  ggrepel::geom_text_repel( x=5, aes(y=label_position, label=label, color = category), size=4) +
  coord_polar(theta="y") +
  xlim(c(-1, 4)) +
  theme_void() +
  # scale_fill_brewer(palette=4) +
  scale_fill_manual(name = '',
                    values = cols) +
  scale_color_manual(name = '',
                     values = cols) +
  theme(legend.position = "none") +
  labs(x = '',
       y = '',
       title = 'Anomalies/errors status')
```

## Fieldworker performance

### Individual

Tanzania
```{r}
left <- tibble(wid = sort(unique(as.character(fids$bohemia_id))))
                
# Join to minicensus
pd <- left %>%
    left_join(
      odk_data$data$minicensus_main %>%
        filter(hh_country == 'Tanzania') %>%
        group_by(wid = as.character(wid)) %>%
        summarise(minicensus = n(),
                  minicensus_days = length(unique(todays_date)))
    )
pd <- pd %>%
  mutate(forms = minicensus,
         days = minicensus_days)
pd <- pd %>%
  mutate(per_day = forms / days) 
pd <- pd %>% filter(!is.na(forms))
pd <- pd %>% arrange(desc(per_day))
pd$wid <- factor(pd$wid, levels = unique(pd$wid))
# save(pd, fids, file = '/tmp/dec2.RData')
right <- fids %>%
  mutate(wid = bohemia_id) %>%
  dplyr::select(wid,first_name, last_name) %>%
  mutate(wid = as.numeric(as.character(wid)))
pd <- left_join(
  pd %>% mutate(wid = as.numeric(as.character(wid))),
  right)%>%
  mutate(wid = paste0(wid,' ', first_name, ' ', last_name))

# remove NA in parantheses
pd <- pd %>% filter(!grepl('NA', wid))
colors <- c('Number of forms' ='blue','Working days'='red')

ggplot(data = pd,
     aes(x = reorder(wid, -per_day),
         y = per_day)) +
geom_bar(stat = 'identity',
         alpha = 0.6) +
labs(x = 'FW',
     y = 'Forms per (working) day') +
theme_bohemia() +
geom_text(aes(label = forms, color='Number of forms'),
          nudge_y = 0.5, size = 3, alpha = 0.8, angle = 90) +
geom_text(aes(label = days, color='Working days'),
          nudge_y = -0.5, size = 3, alpha = 0.8, angle = 90) +
scale_color_manual(name ='', 
                   values =colors) +
theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 5)) +
theme(axis.text = element_text(size = 12),
      axis.title = element_text(size = 14),
      plot.title = element_text(size = 20),
      legend.position = 'top',
      legend.text = element_text(size = 16))

```

Mozambique
```{r}
left <- tibble(wid = sort(unique(as.character(fids$bohemia_id))))
                
# Join to minicensus
pd <- left %>%
    left_join(
      odk_data$data$minicensus_main %>%
        filter(hh_country == 'Mozambique') %>%
        group_by(wid = as.character(wid)) %>%
        summarise(minicensus = n(),
                  minicensus_days = length(unique(todays_date)))
    )
pd <- pd %>%
  mutate(forms = minicensus,
         days = minicensus_days)
pd <- pd %>%
  mutate(per_day = forms / days) 
pd <- pd %>% filter(!is.na(forms))
pd <- pd %>% arrange(desc(per_day))
pd$wid <- factor(pd$wid, levels = unique(pd$wid))
# save(pd, fids, file = '/tmp/dec2.RData')
right <- fids %>%
  mutate(wid = bohemia_id) %>%
  dplyr::select(wid,first_name, last_name) %>%
  mutate(wid = as.numeric(as.character(wid)))
pd <- left_join(
  pd %>% mutate(wid = as.numeric(as.character(wid))),
  right)%>%
  mutate(wid = paste0(wid,' ', first_name, ' ', last_name))

# remove NA in parantheses
pd <- pd %>% filter(!grepl('NA', wid))
colors <- c('Number of forms' ='blue','Working days'='red')

ggplot(data = pd,
     aes(x = reorder(wid, -per_day),
         y = per_day)) +
geom_bar(stat = 'identity',
         alpha = 0.6) +
labs(x = 'FW',
     y = 'Forms per (working) day') +
theme_bohemia() +
geom_text(aes(label = forms, color='Number of forms'),
          nudge_y = 0.5, size = 5, alpha = 0.8, angle = 90) +
geom_text(aes(label = days, color='Working days'),
          nudge_y = -0.5, size = 5, alpha = 0.8, angle = 90) +
scale_color_manual(name ='', 
                   values =colors) +
theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 5)) +
theme(axis.text = element_text(size = 12),
      axis.title = element_text(size = 14),
      plot.title = element_text(size = 20),
      legend.position = 'top',
      legend.text = element_text(size = 16))

```

### Aggregate

Tanzania
```{r}
# Join to minicensus
pd <- odk_data$data$minicensus_main %>%
  group_by(todays_date) %>%
  filter(hh_country == 'Tanzania') %>%
  summarise(minicensus = n(),
            minicensus_workers = length(unique(wid))
)

pdx <- pd %>% mutate(forms = minicensus,
                      workers = minicensus_workers)

pdx <- pdx %>%
  mutate(per_worker = forms / workers) %>%
  mutate(label = paste0(forms, '    ',
                        workers, ''))
pdx <- pdx %>% filter(!is.na(forms))
pdx <- pdx %>% arrange(desc(per_worker))
ggplot(data = pdx,
       aes(x = reorder(todays_date, -per_worker),
           y = per_worker)) +
  geom_bar(stat = 'identity') +
  labs(x = 'FW',
       y = 'Forms per worker',
       caption = 'Numbers show forms on top, workers that day on bottom.\nA "working day" is a day on which that worker submitted any form of that type.') +
  theme_bohemia() +
  geom_text(aes(label = label),
            nudge_y = 0, size = 3, alpha = 0.8,
            angle = 90) +
  theme(axis.text.x = element_text(angle = 90, hjust = 0, vjust = 0.5, size = 6)) +
  theme(axis.text = element_text(size = 12),
        axis.title = element_text(size = 14),
        plot.title = element_text(size = 20),
        plot.caption = element_text(size = 14))

      
```

Mozambique
```{r}
# Join to minicensus
pd <- odk_data$data$minicensus_main %>%
  group_by(todays_date) %>%
  filter(hh_country == 'Mozambique') %>%
  summarise(minicensus = n(),
            minicensus_workers = length(unique(wid))
)

pdx <- pd %>% mutate(forms = minicensus,
                      workers = minicensus_workers)

pdx <- pdx %>%
  mutate(per_worker = forms / workers) %>%
  mutate(label = paste0(forms, '    ',
                        workers, ''))
pdx <- pdx %>% filter(!is.na(forms))
pdx <- pdx %>% arrange(desc(per_worker))
ggplot(data = pdx,
       aes(x = reorder(todays_date, -per_worker),
           y = per_worker)) +
  geom_bar(stat = 'identity') +
  labs(x = 'FW',
       y = 'Forms per worker',
       caption = 'Numbers show forms on top, workers that day on bottom.\nA "working day" is a day on which that worker submitted any form of that type.') +
  theme_bohemia() +
  geom_text(aes(label = label),
            nudge_y = 0, size = 3, alpha = 0.8,
            angle = 90) +
  theme(axis.text.x = element_text(angle = 90, hjust = 0, vjust = 0.5, size = 6)) +
  theme(axis.text = element_text(size = 12),
        axis.title = element_text(size = 14),
        plot.title = element_text(size = 20),
        plot.caption = element_text(size = 14))

      
```



