---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ento


<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.height = 6.5,
  fig.path = 'figures/')
```

# ento: The R package of the Bohemia entomology protocol

This package contains utilities used by the Bohemia entomology research team. It is publicly available for the purposes of reproducibility and transparency.

## Installation

One can install directly from github:

```{r, eval = FALSE}
devtools::install_github('databrew/bohemia', subdir = 'rpackage/ento', dependencies = TRUE, force = TRUE)
```

To remove the package (for example, so as to re-install for an update), simply run: `remove.packages('ento')


```{r setup, include=FALSE, message=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE,
                      fig.width = 4,
                      fig.height = 4)
library(dplyr)
library(tidyr)
library(ggplot2)
library(bohemia)
library(xml2)

# knitr::knit_hooks$set(
#    error = function(x, options) {
#      paste('\n\n<div class="alert alert-danger">',
#            gsub('##', '\n', gsub('^##\ Error', '**Error**', x)),
#            '</div>', sep = '\n')
#    },
#    warning = function(x, options) {
#      paste('\n\n<div class="alert alert-warning">',
#            gsub('##', '\n', gsub('^##\ Warning:', '**Warning**', x)),
#            '</div>', sep = '\n')
#    },
#    message = function(x, options) {
#      paste('\n\n<div class="alert alert-info">',
#            gsub('##', '\n', x),
#            '</div>', sep = '\n')
#    }
# )
```

## Setting up credentials

`cd` into `rpackage/ento/dev` and create a directory called `credentials`. Populate that with your (secret) credentials files, including `bohemiacensuss3credentials.csv`

## Data flow

- Data for this app is read from an AWS S3 bucket. That bucket gets updated by running `scripts/ento/get_ento_forms.R`.  