---
title: "Distances to in Rufiji"
author: "www.databrew.cc"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: "hide"
---


```{r setup, include=FALSE, echo = FALSE}
# Basic knitr options
library(knitr)
opts_chunk$set(comment = NA, 
               echo = TRUE,
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE,
               fig.width = 9.64,
               fig.height = 5.9,
               fig.path = 'figures/')
```

```{r}
## Load libraries
library(ggplot2)
library(lubridate)
library(dplyr)
library(ggplot2)
library(sp)
library(raster)
library(viridis)
library(ggthemes)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(RColorBrewer)
library(readr)
library(zoo)
library(tidyr)
options(scipen = '999')
library(bohemia)
library(geosphere)
```

```{r}
# Define function for calculating distance
calculate_distance <- function(shp, lat, lng){
  p <- c(lng, lat)
  # ll <- length(shp@polygons[[1]]@Polygons)
  ll <- nrow(coordinates(shp))
  out_list <- list()
  for(i in 1:ll){
    temp_points <- coordinates(shp)[i,]#shp@polygons[[1]]@Polygons[[ll]]@coords
    out_list[[i]] <- temp_points
  }
  the_points <- do.call('rbind', out_list)
  the_line <- SpatialPointsDataFrame(coords = the_points,
                                     data = data.frame(id = 1:nrow(the_points)))
  proj4string(the_line) <- proj4string(shp)
  i = 1
  out <- rep(NA, nrow(the_points))
  for(i in 1:nrow(the_points)){
    out[i] <- distm(c(the_points[i,]), c(lng, lat), fun = distHaversine)
  }
  df <- data.frame(the_points)
  df$distance <- out
  df$lng <- lng
  df$lat <- lat
  return(df)
}
```


```{r}
# Define function for drawing
draw <- function(df,
                 shp,
                 n = 20){
  shp_fort <- fortify(shp, id = NAME_2)
  sub_df <- dplyr::sample_n(df, size = n)
  
  g1 <- ggplot() +
    geom_polygon(data = shp_fort,
         aes(x = long,
             y = lat,
             group = group)) +
    geom_segment(data = sub_df,
                 aes(x = x,
                     y = y,
                     xend = lng,
                     yend = lat)) +
    geom_text(data = sub_df,
              aes(x = x,
                  y = y,
                  label = round(distance / 1000, digits = 2)))
  
  g2 <- ggplot(data = df,
               aes(x = distance/1000)) +
    geom_density() +
    labs(x = 'Km',
         y = 'Density',
         title = paste0('Max: ', round(max(df$distance)/1000, 2)))
  Rmisc::multiplot(g1, g2, cols = 2)
}
```

```{r}
# Read in hamlets locations
gps_sp <- gps <- bohemia::gps %>% filter(!is.na(lng)) %>%
  mutate(x = lng, y = lat)

# Get centroids by ward
gps_tza <- gps_sp %>%
  left_join(bohemia::locations %>% dplyr::select(code, District)) %>%
  filter(District == 'Kibiti DC') %>%
  group_by(ward) %>%
  summarise(lng = mean(lng),
            lat = mean(lat)) %>%
  mutate(x = lng, y = lat)

coordinates(gps_tza) <- ~x+y

# gps_tza <- gps_sp[gps_sp@data$iso == 'TZA',]


# Calculate distances



df_tza <- calculate_distance(shp = gps_tza,
                         lng = 38.984170,
                         lat = -7.947843)
df_tza$ward <- df_tza$code <- gps_tza@data$ward
df_tza$lat <- gps_tza@data$lat
df_tza$lng <- gps_tza@data$lng
```

```{r}
# Function to chart distances
chart_distances <- function(df){
  g <- ggplot(data = df,
         aes(x = distance / 1000)) +
    geom_histogram(alpha = 0.6,
                   fill = 'lightblue',
                   color = 'black') +
    databrew::theme_simple() +
    labs(x = 'Kilometers from HQ',
         y = 'Wards')
  return(g)
}

chart_distances_people <- function(df){
  out_list <- list()
  for(i in 1:nrow(df)){
    out <- data.frame(km = df$distance[i] / 1000,
                      id = 1:df$n_households[i])
    out_list[[i]] <- out
  }
  out <- bind_rows(out_list)
  
  g <- ggplot(data = out,
         aes(x = km)) +
    geom_histogram(alpha = 0.6,
                   fill = 'lightblue',
                   color = 'black') +
    databrew::theme_simple() +
    labs(x = 'Kilometers from HQ',
         y = 'Households')
  return(g)
}

chart_distances_xy <- function(df){
  out <- df %>%
    mutate(km = distance / 1000) %>%
    arrange(km) %>%
    mutate(dummy = 1) %>%
    mutate(cs = cumsum(dummy)) %>%
    mutate(p = cs / sum(dummy) * 100) %>%
    group_by(km) %>%
    summarise(p = max(p))
  
  g <- ggplot(data = out,
         aes(x = km,
             y = p)) +
    geom_area(alpha = 0.6,
                   fill = 'lightblue',
                   color = 'black') +
    databrew::theme_simple() +
    labs(x = 'Kilometers from HQ',
         y = '% of wards within this distance') +
    geom_hline(yintercept = seq(0, 100, by = 25),
               alpha = 0.3) +
    geom_vline(xintercept = max(out$km))
  return(g)
}


chart_distances_people_xy <- function(df){
  out_list <- list()
  for(i in 1:nrow(df)){
    out <- data.frame(km = df$distance[i] / 1000,
                      id = 1:df$n_households[i])
    out_list[[i]] <- out
  }
  out <- bind_rows(out_list) %>%
    arrange(km) %>%
    mutate(dummy = 1) %>%
    mutate(cs = cumsum(dummy)) %>%
    mutate(p = cs / sum(dummy) * 100) %>%
    group_by(km) %>%
    summarise(p = max(p))
  
  g <- ggplot(data = out,
         aes(x = km,
             y = p)) +
    geom_area(alpha = 0.6,
                   fill = 'lightblue',
                   color = 'black') +
    databrew::theme_simple() +
    labs(x = 'Kilometers from HQ',
         y = '% of households within this distance') +
    geom_hline(yintercept = seq(0, 100, by = 25),
               alpha = 0.3) +
    geom_vline(xintercept = max(out$km))
  return(g)
}

# Lealet map
library(leaflet)
make_leaf <- function(df){
  # mapview::mapview() %>%
    leaflet() %>%
    addProviderTiles(providers$OpenStreetMap) %>%
    addMarkers(data = df,
               popup = paste0(df$code, ' (', df$hamlet, '), ',
                              round(df$distance/1000, digits = 1),
                              ' km')) 
}

make_leaf_cocentric <- function(df){
  # use one coordinate to detect country
  lat <- df$lat[1]
  if(lat <= -12){
    iso <- 'MOZ'
    hq <- data.frame(lng = 35.711553, lat = -17.979446)
  } else {
    iso <- 'TZA'
    hq <- data.frame(lng = 38.984170, lat = -7.947843)
  }
  
  # Make hq spatial
  hq_sp <- hq %>% mutate(x = lng, y = lat)
  coordinates(hq_sp) <- ~x+y
  
  proj4string(hq_sp) <- CRS("+init=epsg:4326") # define as lat/lng
  zone <- 36
  # Project
  new_proj <- CRS(paste0("+proj=utm +zone=", 
                       zone, 
                       " +south +ellps=WGS84 +datum=WGS84 +units=m +no_defs"))
  hq_sp <- spTransform(hq_sp,
                       new_proj)
  
  l <- leaflet() %>%
    addProviderTiles(providers$OpenStreetMap) %>%
    addMarkers(data = hq)
  
  # Get cocentric circles
  distances <- c(10, 20, 50)
  cols <- rainbow(length(distances))
  counter <- 0
  for(i in distances){
    counter <- counter +1
    the_name <- paste0('c', i)
    the_distance <- paste0(i, ' km radius')
    the_poly <- spTransform(rgeos::gBuffer(hq_sp, width = i * 1000), CRS("+init=epsg:4326"))
    assign(the_name, 
           the_poly)
    l <- l %>%
      addPolylines(data = the_poly,
                   popup = the_distance,
                   color = cols[counter])
  }
  l <- l %>%
    addCircleMarkers(data = df,
                     popup = paste0(df$code, ' (', df$hamlet, '), ',
                                    round(df$distance/1000, digits = 1),
                                    ' km'),
                     color = 'black',
                     fillColor = 'black',
                     opacity = 0.8,
                     radius = 3)
  return(l)
}
library(class)
library(cluster)
make_knn <- function(df){
 kmeans2 <- kmeans(x = df[,c('lng', 'lat')], centers = 6, nstart = 25)
  pd <- df
  pd$cluster <- kmeans2$cluster
  n_cols <- max(pd$cluster)
  cols <- rainbow(n_cols)
  l <- leaflet() %>%
    addTiles() %>%
    addCircleMarkers(data = pd,
                     color = cols[pd$cluster],
                     popup = paste0(pd$code, ' ',
                                    '(',
                                    pd$hamlet,
                                    '), team: ',
                                    pd$cluster),
                     radius = 2)
  return(l)
}

```


# Distance to headquarters from Kibiti wards {.tabset}


## Tanzania


```{r}
df <- df_tza
```



The below chart shows the distribution of distances from headquarters. The x-axis is distance in kilometers (as the crow flies) from HQ, and the y-axis is the number of wards at that distance.

```{r}
chart_distances(df = df)
```

### Percentage of wards within X kilometers 

The below chart shows what percentage of wards (y-axis) are located at or less kilometers (x-axis) from headquarters.

```{r}
chart_distances_xy(df = df)
```

### Interactive map of ward centroids

The below map shows all ward locations, per recon, using the centroid method of hamlets. It is interactive (you can zoom in/out, or click on a hamlet for more information).

```{r}
make_leaf(df = df)
```


### Interactive map of cocentric distance circles

The below map shows all wards locations, per recon. It is interactive (you can zoom in/out, or click on a ward for more information). The cocentric radial circles are drawn at 10km, 20km, and 50km.

```{r}
make_leaf_cocentric(df = df)
```

### Table

```{r}
pd <- df %>%
  mutate(km = distance / 1000) %>%
  dplyr::select(ward, km)
bohemia::prettify(pd,
                  nrows = nrow(pd))
```