---
title: "Recon report"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: "hide"
---


```{r setup, include=FALSE, echo = FALSE}
# Basic knitr options
library(knitr)
opts_chunk$set(comment = NA, 
               # echo = FALSE, 
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE,
               fig.width = 9.64,
               fig.height = 5.9,
               fig.path = 'figures/')
```

```{r}
## Load libraries
library(bohemia)
library(ggplot2)
library(lubridate)
library(dplyr)
library(ggplot2)
library(leaflet)
library(sp)
library(raster)
library(ggthemes)
library(sf)
library(RColorBrewer)
library(readr)
library(tidyr)
# options(scipen = '999')
theme_set(databrew::theme_simple())
```

```{r}
# download from https://trello.com/c/mPDK9j47/2313-bohemia-network-coverage-maps-using-recon-data-internet-plus-each-provider
load('recon.RData')

# load location hierarchy 
gps_locations <- read.csv('location_hierarchy.csv')

# join with recond_data on hamlet code
recon_data <- left_join(recon_data, gps_locations, by=c('hamlet_code'='code'))

# remove .x and .y columns
names(recon_data) <- gsub('.y', '', names(recon_data), fixed = TRUE)
recon_data <- recon_data[, !grepl('.x', names(recon_data), fixed = TRUE),]

# subset by country
tz_recon <- recon_data %>% filter(Country =='Tanzania')
mz_recon <- recon_data %>% filter(Country =='Mozambique')


rm(animal, animal_xls, chiefs, fids, recon_xls, gps_locations, recon_data)

# create function for mapping points for phone and internet variables
map_coverage <- function(temp, column_name,legend_title){
  temp <- temp %>% dplyr::select('lat','lng', 'Hamlet' ,column_name)
  names(temp)[4] <- 'plot_var'
  temp$plot_var <- gsub("^$|^ $", NA, temp$plot_var)
  temp$plot_var <- factor(temp$plot_var,
                          levels = c('No', 'DK', 'Yes'))
  pal_map <- colorFactor(palette = brewer.pal(n= length(unique(temp$plot_var)), 
                                                name = 'Spectral'), domain = temp$plot_var)
  leaflet(temp) %>% 
    addTiles()  %>% 
    addCircleMarkers(lng =~lng, 
                     lat =~lat,
                     color = ~pal_map(plot_var),
                     radius = 5,
                     popup = ~unname(Hamlet),
                     stroke = TRUE, 
                     fillOpacity = 0.5) %>%
    addLegend(pal = pal_map, values = ~plot_var,position = "bottomleft", title = legend_title) 
  # 
}


# create function for mapping points for phone and internet variables
map_summary <- function(temp, column_name,legend_title){
  temp <- temp %>% dplyr::select('lat','lng', 'Hamlet' ,column_name)
  names(temp)[4] <- 'plot_var'
  temp$plot_var <- gsub("^$|^ $", NA, temp$plot_var)
  levs <- c('No', 'DK', 'Yes')
  levs <- levs[levs %in% unique(temp$plot_var)]
  temp$plot_var <- factor(temp$plot_var,
                          levels = levs)
  pal_map <- brewer.pal(n= 3, name = 'Spectral')
  if(!'DK' %in% levs){
    pal_map <- pal_map[c(1, 3)]
  }
  pd <- temp %>%
    group_by(plot_var) %>%
    tally
  
  ggplot(data = pd,
         aes(x = plot_var,
             y = n,
             group = plot_var)) +
    geom_bar(stat = 'identity',
             aes(fill = plot_var)) +
    scale_fill_manual(name = '',
                      values = pal_map) +
    geom_text(aes(label = n,
                  y = 0),
              nudge_y = 10) +
    labs(x = 'Status',
         y = 'Hamlets',
         subtitle = 'Summary') +
    theme(legend.position = 'none')
}



# Ideas:
# - Map of yes/no phone coverage
# - Map of yes/no any internet coverage
# - Vodafone internet map
# - Vodafone phone map
# - Mcell internet map
# - etc.
# - Best network by area
# 
# Advanced ideas:
# - Smoothing and polygonation
# 
# Other things:
# - Bar charts / aggregate stuff (number of hamlets with each type, etc.).
```

# Coverage report {.tabset}

This report contains maps and tables showing internet and phone coverage, overall and by provider types, for each hamlet of the Bohemia research area.


## Tanzania coverage maps

### All internet coverage

```{r}
map_summary(tz_recon, 'telecom_have_data', legend_title = 'Internet coverage')

map_coverage(tz_recon, 'telecom_have_data', legend_title = 'Internet coverage')
```

### All phone coverage

```{r}
map_summary(tz_recon, 'telecom_have_voice', legend_title = 'Voice coverage')

map_coverage(tz_recon, 'telecom_have_voice', legend_title = 'Voice coverage')
```

### Vodafone internet coverage

```{r}
map_summary(tz_recon, 'telecom_work_data_vodacom', legend_title = 'Vodaphone internet coverage')

map_coverage(tz_recon, 'telecom_work_data_vodacom', legend_title = 'Vodaphone internet coverage')
```

### Vodafone phone coverage

```{r}
map_summary(tz_recon, 'telecom_work_voice_vodacom', legend_title = 'Vodaphone phone coverage')


map_coverage(tz_recon, 'telecom_work_voice_vodacom', legend_title = 'Vodaphone phone coverage')
```


### Tigo internet coverage

```{r}
map_summary(tz_recon, 'telecom_work_data_tigo', legend_title = 'Tigo internet coverage')

map_coverage(tz_recon, 'telecom_work_data_tigo', legend_title = 'Tigo internet coverage')
```


### Tigo phone coverage

```{r}
map_summary(tz_recon, 'telecom_work_voice_tigo', legend_title = 'Tigo phone coverage')


map_coverage(tz_recon, 'telecom_work_voice_tigo', legend_title = 'Tigo phone coverage')
```

### TTCL internet coverage

```{r}
map_summary(tz_recon, 'telecom_work_data_ttcl', legend_title = 'TTCL internet coverage')


map_coverage(tz_recon, 'telecom_work_data_ttcl', legend_title = 'TTCL internet coverage')
```

### TTCL phone coverage 

```{r}
map_summary(tz_recon, 'telecom_work_voice_ttcl', legend_title = 'TTCL phone coverage')


map_coverage(tz_recon, 'telecom_work_voice_ttcl', legend_title = 'TTCL phone coverage')
```

### Halotel internet coverage 

```{r}
map_summary(tz_recon, 'telecom_work_data_halotel', legend_title = 'Halotel internet coverage')


map_coverage(tz_recon, 'telecom_work_data_halotel', legend_title = 'Halotel internet coverage')
```

### Halotel phone coverage 

```{r}
map_summary(tz_recon, 'telecom_work_voice_halotel', legend_title = 'Halotel phone coverage')


map_coverage(tz_recon, 'telecom_work_voice_halotel', legend_title = 'Halotel phone coverage')
```

### Airtel internet coverage

```{r}
map_summary(tz_recon, 'telecom_work_data_airtel', legend_title = 'Airtel internet coverage')


map_coverage(tz_recon, 'telecom_work_data_airtel', legend_title = 'Airtel internet coverage')
```

### Airtel phone coverage

```{r}
map_summary(tz_recon, 'telecom_work_voice_airtel', legend_title = 'Airtel phone coverage')



map_coverage(tz_recon, 'telecom_work_voice_airtel', legend_title = 'Airtel phone coverage')
```

## MOZ coverage maps

### All internet coverage

```{r}
map_summary(mz_recon, 'telecom_have_data', legend_title = 'Internet coverage')


map_coverage(mz_recon, 'telecom_have_data', legend_title = 'Internet coverage')
```

### All phone coverage

```{r}
map_summary(mz_recon, 'telecom_have_voice', legend_title = 'Voice coverage')


map_coverage(mz_recon, 'telecom_have_voice', legend_title = 'Voice coverage')
```

### Vodafone internet coverage

```{r}
map_summary(mz_recon, 'telecom_work_data_vodacom', legend_title = 'Vodaphone internet coverage')


map_coverage(mz_recon, 'telecom_work_data_vodacom', legend_title = 'Vodaphone internet coverage')
```

### Vodafone phone coverage

```{r}
map_summary(mz_recon, 'telecom_work_voice_vodacom', legend_title = 'Vodaphone phone coverage')


map_coverage(mz_recon, 'telecom_work_voice_vodacom', legend_title = 'Vodaphone phone coverage')
```

### Mcell internet coverage

```{r}
map_summary(mz_recon, 'telecom_work_data_mcell', legend_title = 'Mcell internet coverage')


map_coverage(mz_recon, 'telecom_work_data_mcell', legend_title = 'Mcell internet coverage')
```

### Mcell phone coverage

```{r}
map_summary(mz_recon, 'telecom_work_voice_movitel', legend_title = 'Movitel voice coverage')


map_coverage(mz_recon, 'telecom_work_voice_movitel', legend_title = 'Movitel voice coverage')
```

### Movitel internet coverage

```{r}
map_summary(mz_recon, 'telecom_work_data_movitel', legend_title = 'Movitel internet coverage')


map_coverage(mz_recon, 'telecom_work_data_movitel', legend_title = 'Movitel internet coverage')
```

### Movitel phone coverage

```{r}
map_summary(mz_recon, 'telecom_work_voice_movitel', legend_title = 'Movitel phone coverage')


map_coverage(mz_recon, 'telecom_work_voice_movitel', legend_title = 'Movitel phone coverage')
```






