---
title: "Recon report"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: "hide"
---


```{r setup, include=FALSE, echo = FALSE}
# Basic knitr options
library(knitr)
opts_chunk$set(comment = NA, 
               # echo = FALSE, 
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE,
               fig.width = 9.64,
               fig.height = 5.9,
               fig.path = 'figures/')
```

```{r}
## Load libraries
library(bohemia)
library(ggplot2)
library(lubridate)
library(dplyr)
library(ggplot2)
library(sp)
library(raster)
library(ggthemes)
library(sf)
library(RColorBrewer)
library(readr)
library(tidyr)
# options(scipen = '999')
theme_set(databrew::theme_simple())
```

```{r}
# download from https://trello.com/c/mPDK9j47/2313-bohemia-network-coverage-maps-using-recon-data-internet-plus-each-provider
load('recon.RData')
# Ideas:
# - Map of yes/no phone coverage
# - Map of yes/no any internet coverage
# - Vodafone internet map
# - Vodafone phone map
# - Mcell internet map
# - etc.
# - Best network by area
# 
# Advanced ideas:
# - Smoothing and polygonation
# 
# Other things:
# - Bar charts / aggregate stuff (number of hamlets with each type, etc.).
```

# Reconnaissance report {.tabset}

## Summary

This report contains maps and tables showing internet and phone coverage, overall and by provider types, for each hamlet of the Bohemia research area.


# Map of yes/no phone coverage

## TZA
```{r}

```
## MOZ
```{r}

```

# Map of yes/no any internet coverage

## TZA
```{r}

```
## MOZ
```{r}

```

# Vodafone internet map

## TZA
```{r}

```
## MOZ
```{r}

```

# Vodafone phone map
## TZA
```{r}

```
## MOZ
```{r}

```


# Mcell internet map (and more)
## TZA
```{r}

```
## MOZ
```{r}

```


# Best network by area
## TZA
```{r}

```
## MOZ
```{r}

```



